
---
title: "Power Analysis for UX/HF Research"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This document demonstrates how to perform power analysis in UX and HF research. Power analysis is used to determine the sample size needed to detect an effect with a specified confidence level and statistical power.

---

## Step 1: Load the Data

```{r load-data}
# Load necessary libraries
library(tidyverse)
library(pwr)

# Load the dataset (assuming it's in the same folder as this Rmd file)
data <- read.csv("power_analysis_data.csv")

# Quick look at the data
head(data)
summary(data)
```

---

## Step 2: Visualize the Data

```{r visualize-data}
# Plot the scores for each group
ggplot(data, aes(x = Group, y = Score, fill = Group)) +
  geom_boxplot() +
  labs(title = "Score Distribution by Group", x = "Group", y = "Score") +
  theme_minimal()
```

---

## Step 3: Perform Power Analysis

### Power Analysis for a Two-Sample t-Test
```{r power-t-test}
# Calculate effect size (Cohen's d)
group_means <- data %>%
  group_by(Group) %>%
  summarise(Mean = mean(Score), SD = sd(Score))

effect_size <- abs(diff(group_means$Mean)) / mean(group_means$SD)
cat("Effect Size (Cohen's d):", round(effect_size, 2), "
")

# Perform power analysis
power_t <- pwr.t.test(d = effect_size, power = 0.8, sig.level = 0.05, type = "two.sample")
cat("Required sample size per group:", ceiling(power_t$n), "
")
```

### Power Analysis for ANOVA
```{r power-anova}
# Perform power analysis for one-way ANOVA
anova_effect_size <- 0.25  # Medium effect size (Cohen's f)
power_anova <- pwr.anova.test(k = 2, f = anova_effect_size, power = 0.8, sig.level = 0.05)
cat("Total required sample size for ANOVA:", ceiling(power_anova$n), "
")
```

---

## Step 4: Interpret Results

- **Effect Size (Cohen's d)**: Indicates the magnitude of the difference between groups.
- **Sample Size for t-Test**: The number of participants needed in each group to detect the effect with 80% power and a 5% significance level.
- **Sample Size for ANOVA**: Total number of participants needed to detect a medium effect size.

---

## Conclusion

This document demonstrates how to perform power analysis for common statistical tests in UX/HF research. You can adjust the effect size, power, and significance level based on your study's needs.
